---
title: "Introduction to gtrendsR"
author: "Philippe Massicotte and Dirk Eddelbuettel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo = FALSE}
library(gtrendsR)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 5, fig.height = 3, fig.align = 'center')
```


In version v2.0.0, `grendsR` gets a major revamping due to change in Google Trends API. One of the major difference is that login into a Google account is no longer requiered to perform queries.

## Data structure

```{r}
res <- gtrends("NHL")
str(res$interest_over_time)
str(res$interest_by_region)
```


## Countries

## Categories

## Working with time

| Keywords          | Time span                             |
|------------------:|:--------------------------------------|
| now 1-H           | Last hour                              |
| now 4-H           | Last four hours                        |
| now 1-d           | Last day                               |
| now 7-d           | Last seven days                        |
| today 1-m         | Past 30 days                           |
| today 3-m         | Past 90 days                           |
| today 12-m        | Past 12 months                         |
| today+5-y         | Last 5 years (default)                 |
| all               | Since begening of Google Trends (2004) |


### Examples

```{r}
res <- gtrends("NHL", time = "now 1-H")

plot(res)
```



